---
title: "Homework5"
author: "Annie Yu"
date: "11/2/2018"
output: github_document
---

```{r setup, message=FALSE}
library(tidyverse)
library(purrr)
library(rvest)
library(reshape2)

```
##Problem 1
### Create a tidy dataframe 
```{r , message=FALSE}
long_study <- list.files('/Users/annie/Desktop/data science/Homework/homework5/Homework 5/data')  

df_longstudy <- function(x){
   read_df<- read_csv(paste0('/Users/annie/Desktop/data science/Homework/homework5/Homework 5/data/', x))
   read_df
}

output= map(long_study, df_longstudy)
week_results = bind_rows(output)

read_df<-long_study %>% 
  str_replace('.csv', '') 

df<-as.data.frame(read_df) 

longstudy<-
  cbind(df, week_results) %>% 
  gather(key = week, value = value, week_1:week_8) %>% 
  mutate(week = str_replace(week, 'week_', '')) %>% 
  mutate(week = as.numeric(week)) %>% 
  separate(read_df, into = c("arms", "id"),sep = "_") 

  
```

### Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r}
ggplot(longstudy, aes(x= week, y = value, color=id))+
  facet_grid(~as.factor(arms))+
  geom_line()+
  labs(
    title = "The Difference Between Control Group and Experiment Gruop",
    x = "Weeks",
    y = "Value"
  )+
  viridis::scale_color_viridis(
    discrete = TRUE
  ) + 
  theme(legend.position = "bottom")
  
```

##Problem 2

###Reading，adding variable，and summarize total number and unsolved number of homicides
```{r, message=FALSE}
homicide = read_csv('/Users/annie/Desktop/data science/Homework/homework5/Homework 5/homicide-data.csv') 

homicide %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(homicide$city,",",homicide$state))

total_homicides <-
  homicide %>% 
  group_by(city) %>% 
  summarize(total = n(),
            unsolved = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest")) %>% 
  ungroup()

  
```


###For the city of Baltimore, MD， estimate the proportion of homicides that are unsolved
```{r}
baltimore_total <- subset(total_homicides, city =="Baltimore")$total
baltimore_unsolved <- subset(total_homicides, city == "Baltimore")$unsolved

prop_ba_unsolved <- prop.test(baltimore_unsolved, baltimore_total) %>% 
  broom::tidy() %>% 
  janitor::clean_names() %>% 
  select(estimate, conf_low, conf_high)

knitr::kable(prop_ba_unsolved)

  
```


###Calculate for each of the cities, and extract both the proportion of unsolved homicides and the confidence interval for each

```{r}
prop_hom = function(x){
   prop.test(x$unsolved, x$total) %>% 
   broom::tidy() %>%  
   janitor::clean_names() %>% 
   select(estimate, conf_low, conf_high)
}

all_prop <- nest(total_homicides, total:unsolved) %>% 
  mutate(result = map (data, prop_hom)) %>% 
  unnest()

as.tibble(all_prop)


```

###The plot of estimates and CIs for each city
```{r}
all_prop %>% 
  ggplot(aes(x= reorder(city, -estimate), y = estimate))+
  geom_point()+
  geom_errorbar(aes(x = city, ymin = conf_low, ymax = conf_high))+
  labs(
    title = "The plot of estimates and CIs for each city",
    x = "City",
    y = "Estimate with CI"
  )+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1), legend.key.width = unit(0.15,'cm'))
  
  
```

